\section{A Mere Memory}
“Luke, you can't stay like this forever!”

A chill went through my veins. My eyes snapped open, but I could only see darkness.

There was a laugh as someone grabbed my hand, attempting to pull me out of the slide.

“It's alright. Accept what happened and move on. Cheer up! No need to hide!”

As I was lifted, a sliver of light shined into me. That voice, it sounded like her. I wanted to call her name. Tell her I was glad she was back. But my voice stuck in my throat.

With another tug, she pulled me out of the slide.

“Got you out!” she laughed, pulling me out and laid me on the playground metal. She inspected my face up close with her dark, brown eyes. “This is like fishing,” she said, poking me.

The sun shined into my face. It felt warm, but also wrong. Like it was wrong to enjoy it.

“Isn't this so much better?” she asked, running her fingers through my hair. “It's so much brighter, so much prettier than that dark slide…” she said, waving her hand towards the orange sunset.

My eyes wandered to a swing, a group of children.

They laughed, talking to each other while swinging on the seats. It stirred something in my mind. They appeared  like they were there, but they weren't there. Not anymore. 

I gripped her hand, shivering.

“Geez, you're stubborn,” she commented. “How about this?” she asked. She snapped her fingers. 

In an instant, the light morphed into a warm, comfortable ray, like a sunny day with perfect wind and temperatures. The sensation was like being wrapped in a warm blanket during the cold winter.

I rolled over to face the sun, loosening my grip.

“Does it feel nicer?” she asked.

I nodded.

“You still haven't moved on…” She closed her eyes and sighed, shaking her head and giving me a sad smile. “It's sweet and all, but you can't just keep holding to things that are gone. You've got to find something new. You told me, didn't you? ‘A place far away'. That was your goal, wasn't it? It's chaseable, isn't it? It's that new light.”

Her words cut into my heart, reminding me of something I had once said. 

The sun seemed to be moving downwards faster, light leaving the sky as it was dragged below the horizon by an invisible force.

She opened her eyes, looking around. “It's ending already…” she grumbled, turning her eyes back at me. “You know what to do, don't you? We don't have much time left. That's why… You have to move on. It's already been a year.”

As she said that, the light faded, cold air blew into me. The darkness slowly creeped up, engulfing all. Everything was disappearing. 

A reminder that none of this is real. A mere dream. A hallucination. 

“Amira, please…” my voice cracked. “Don't leave me again.” I squeezed out. 

Amira smiled sadly, before fading out, leaving me alone in the cold darkness. 

I shivered, surrounded by my own fears. I didn't want a new light. I longed for that light again. Her light again. 

I closed my eyes as the ice, sharp pain of reality washed over me.

That light was gone forever. It won't come back. It couldn't  be undone.

A proof that nothing will ever last.

A tear rolled down my cheeks.







