%% Chapter 5 %%
\section{Castles are the Hell}
I brushed the dust off the photo frames.

Lifting one up, it was a picture of Princess, Ken, Tam, Amira, and I at a playground.

As the others played on the swings, Amira was poking my face, telling me to cheer up. 

“Luke, you’ve got to look at the bright side more,” she had said.

Just then, there was a knock on my door.

“Luke? Are you at home?” a voice called.

I placed the frame facedown, before moving to the door. When I opened it I was greeted with a face that I would last expect.

“P-Parker?”

“Greetings, Luke,” Parker said. 

“W-.” I took a breath. “What brings you here?”

“Just wanted to stop by,” he said, fanning his face. “Ironically, the overall economy of WINGS I has been dropping.” Weirdly, he said it with a smile on his face.

WINGS I. The official name for this underground place, ironically opposite of flying.

“Economy?”

“Yeah,” Parker replied. “But it’s because many others have been heading above.”

“Others have been heading above?”

“I guess they saw that you went up, and decided to give it a try as well.”

“Oh… Interesting.”

Parker closed his eyes.

“You know, WINGS I has 15 members, including you and Fayes. It’s a lot smaller than the other WINGS.”

“How much do the other WINGS have?”

“Around 40. Don’t have the exact numbers.”

“Oh…”
“But it’s not what you think.” Parker opened his eyes and stared at the ceiling. “I don’t believe that this underground network can be called a place to live. I run this place, not as a home, but as a shelter for those to one day return above. That’s why, I’m glad that people are returning. Even if it means our population is diminishing.”

I opened my mouth, but nothing came out.

Parker looked back at me. “Thank you, Luke. I’ll see you around.”

I watched him as he walked away.

Above.

His belief is why there was so much emphasis on heaven being above.

Was the above heaven? I haven’t found anything heaven-like above.

I looked at the pushed down frames.

A heaven was once above. It shattered. Vanished. Leaving nothing but remains of sharp glass, that does nothing but leave bitterness. Yet ironically, once broken, it was impossible to bring back the glass together.

Of course, in that analogy, there existed many technologies that could reforge glass together. So maybe…

I stared towards the end of the hall.

Something left to save. A chance for us to be together again.

I took out my IDS and activated the holographic screen.

[Screen]
January 11, 2051, 6:31 PM
Welcome back, Luke. 

Swipe up to unlock.
[Screen]

I swiped up and entered ‘PRINCESS.14’.

The background replaced itself with the image of me, Amira, Princess, and Tam at the park.

Unlike last time, there was only the hollowness. And a sharp feeling of… longing.

That day…

You should’ve been too.

I turned back. The knife lying on my nightstand suddenly looked like a weapon. I could almost imagine it being covered with blood. 

A shiver ran through me.

I walked over, picking it up. In the reflection of the metal, I could see a reflection. Luke. Me.

A pain burned in my finger. A vague memory flashed in my mind. 

A girl ran over to her brother, who tried to help her cut the vegetables for dinner.

“Luke, are you alright?” she asked, before seeing red on his fingers. She observed them. “Did you cut yourself?”

The boy, Luke nodded. He was holding back from shaking in pain.

The girl, Amira, cleaned the wound, while Luke gripped her hand. Afterwards, she put a bandage on the wound. “It’s all fine now,” she reassured him.

Luke nodded, but without ever letting go of her hand. The sight of the knife left a feeling of uncomfort. Whenever he saw it, he would feel uncomfortable. The uncomfortable feeling and fear would prove itself rational when REVER-.

I cut off the thought, before lifting my hand and observing the same spot I had cut. A pinkish, extruding scar remained where it was. A scar that remained longer than her.

As I stared at the knife, a sudden, familiar, uncomfortable feeling stirred in me. Awoke again. 

I quickly stuck the knife into my bottom drawer. A part of me wondered why I bought the knife. I took a deep breath to settle my nerves. 

Sliding on my hood, I put my IDS into my pocket and headed out of my room.

As I was walking in the gray halls, I reached into my pocket, and felt a can.

The can of karocel. There were four pills in it. Surprisingly, I hadn’t eaten any more.

When I approached the gates to the above, Parker was nowhere in sight. He seldom ever was at that desk.

As I pushed the gates open, a voice called out from behind me. 

“Luke, is that you?”

I turned around to find Fayes. Fayes Drake
“... Hello Fayes.”

Fayes walked up to me and looked at where my hands were resting. On the gates.

“Are you planning to head above?” he asked.

“Yeah…”

“How coincidental,” he remarked, scratching the back of his head. “I was planning to do so too.”

I nodded, turning back and climbing up the stairs.

Fayes followed behind me, as we took our steps to the above. Ibis City. When we stepped out of the bathroom, the same city stretched in front of us.

“Another day to be alive,” Fayes muttered.

I took a step forward. “... Would you say that’s a good thing?” I asked, staring at the ground.

“You wouldn’t know until you lived it,” he replied.

He was wrong. It was probably possible to find out today’s fortune based on yesterday. But I didn’t say anything as I walked forward.

Fayes and I walked around the city, observing the changes. He was outdated as well, leaving confusion between us whenever we’d see something that was new. The new shops that opened up, some of the new constructions.

Fayes stopped.

“Have you eaten dinner?” he asked, pointing to the clock. “It’s 7 o’clock.”

“...I’m not really that hungry.”

“No? Well, I’m going to get a meal. You might as well get one too.”

“Well…” I thought of the times I slept through my meals.

“Here,” Fayes said. He tossed me an IDS slip, a transferable money card. “I’ll pay for your meal. It’s the least I could pay you back for the time you took me up here.”

If he was going out of his way to give me the meals, I might as well accept it.

“T-thanks…” I stammered as I took the slip. 

He turned away. “No problem,” he said.

We found a concession stand nearby, and ordered some food. Fayes ordered a burger and some fries, and I ordered a hotdog.

“So, how’s things been going?” Fayes asked, tearing a piece of his hamburger. He popped it into his mouth.

The wind blew against my hair, reminding me of how long it was. 

“Nothing special,” I replied, taking a bite of my hotdog. “Just occasional walks up here, that’s all. Maybe a bit of window shopping.”

Fayes closed his eyes, a pained smile on his face. “Window Shopping… I remember when I would always window shop because I was broke.”

We ate in silence.

“There was once a time,” Fayes started. “when I accidentally took out some dice from the store. I slipped some into my pocket, and accidentally took it out.”

“Huh. They didn’t stop you?”

“No they did. I took it out of the store, opened it, thinking I had bought it. Then the guards showed up, demanding it back.”
“You gave it back?”

Fayes scratched his head. “I… I’m not so sure,” he said. “Somehow, I can’t recall the next part. It’s fuzzy.”

Something about his line intrigued me. “Did the memory come in bits or all at once?” I asked.

“Somehow… the first part clicked when you mentioned window shopping.“

I had an urging feeling that the subject he was talking about could lead to deep water. Clicked on keywords. Fuzzy. The thing to me that was like that was…

I sucked in a breath as I pondered whether or not I should press him. His face wandered in confusion, probably trying to remember. But if it was really like my case, it was probably better to not say anything. Even so, I was curious, admittedly.

“Perhaps… the guards let you off?”

Fayes scratched his chin. “No, I don’t think that happened. It doesn’t ring a bell.”

“Perhaps you had money on you to pay them?”

“No, I was like, 10, I didn’t have any money, let alone enough to pay it off.”
“Maybe someone else paid for it?”

As he sipped from his drink, he choked on his water. Coughing and gagging he snatched a napkin and wiped his mouth with it. His face darkened, and the smile wiped off his face.

Something told me to end the talk right there.

“Are you alright?” I asked.

“...I’m fine,” Fayes replied. His eyes were lacking the smile he used to bear. 

“W-well, how was your meal?” I asked, looking at his one-fourth remaining burger.

“It was alright,” he replied, staring into his hands.

I nodded, looking away to give him some space. Maybe I shouldn’t have said anything earlier.

The city lights of red, green, blue, and purple flashed in the buildings. People hurried their way across the streets, across the bridges. Rushing home from work. 

“Luke?”

I turned back to see Fayes staring at me.

“You’ve never told me your full name,” he said, brushing some dust off his chair. “Fayes Drake, that’s who I am.”

The wind blew my hair across my face, covering my eyes. Evans. Something about the name felt wrong, yet it was my last name. 

I closed my eyes. “Evans. Luke Evans.

“Luke Evans?” Fayes asked. “It seems like a familiar name…” he scratched his chin in thought. “Luke Evans,” he repeated, over and over again to himself.

At that moment, a young, smooth voice called out from behind me.

“Umm, excuse me, but do you go by the name ‘Luke Evans’?”

I turned around to find a person standing behind me. They wore a light, gray jacket with the hood on, concealing part of their face. Immediately, something felt familiar about the figure.

“Y-yes, I am Luke Evans,” I said, hesitation clouding my mind. I wasn’t sure if anyone could still recognize me from the news, but there was still doubt.

The figure backed off, their hood falling off. I could get a clever vision of their face.

My eyes widened.

 This… this…

Her dark, brown hair stretched and twirled down to her chest. Her amber eyes widened as they flickered, just as shocked as I was.

“L-Luke isn’t it?” Princess stuttered. “It’s been a while, hasn’t it?”