\section{Heaven is Above, not Below}
A building stretched above me.

The STARLIGHT building. One of the central towers in Ibis City. Several hundred meters tall, it was the tower for commercial businesses, with an extreme apartment complex above.

“One day, we’ll be up there! Together!” Tam had once said in the past. A warm, sunny, picnic day.

Princess, Amira, Ken, and I laughed. It was a joke. We would never have the money for one of those apartments, and if we did, by the time we do, we’ll probably forget about this.

But it was a funny joke. We all liked being above the ground. Born in Ibis City, where one sees the world like an ibis bird, a birds-eye view of the world. Up and above, where one can see everything. All the buildings, all the people.

Ironically, I ended up below the ground.

I turned back towards the park.

Navigating my way back, I pushed open the gate and walked back down the stairs..

A chance for us to be together again.

“Luke!”

A familiar voice called to me. Parker. From his desk, he wore the same clothes from days ago. The black T-shirt, Heaven was above, not below.

“Out above lately?” he asked, shutting off the holographic screen.

“... Just a few walks. Nothing more.”

“Wow,” he said, scratching his chin. “You would be the last person I’d expect to have headed above.”

As he said that, a boy standing at the edge of the table coughed. The moment I saw him, I recognized him. The same boy that told me directions for the rent booth. The same blond, curly hair. His shirt was plain black, not a single other color.

Before I had a chance to say something, he interrupted.

“Aren’t you that guy that asked for directions to a rent booth? A few days ago?”

I opened my mouth, but I couldn’t think of anything to say. 

Parker laughed. “He’s Luke,” he said, pointing to me. “This is Fayes.”

Fayes observed me. “Luke. That’s your name?” he asked.

“Luke,” I repeated. “Yes.”

A moment of silence etched. As I stared into his eyes, I couldn’t help but feel a connection. A similarity.

It was special about this underground place. The fact that we’re still alive. The fact that we’re both down here. The fact that we’ve run from above. Away from reality. In some sense, I could see through, see into him. Like with the people I see here. After all, the ones that have come here all shared that.

Fayes coughed, turning away.

Parker laughed, before scrolling open a drawer. He took out a silver square, a stamp, and handed it to Fayes.

“Your transaction is finished. Take the receipt print coin.”

Fayes took the coin, sliding it into his pocket.

“You guys…” Parker sat back in his chair and stared at the roof of the ceiling. “Ibis City… I haven’t been there in quite a long time,” Parker mumbled, taking out a cigarette. After lighting it, he puffed out some smoke.

“Is there something stopping you?” Fayes asked.

“Several things. Partly because of my workload. But also, some part of me doesn’t want to.”

Like all of us here. The master shouldn’t be any different.

Fayes shifted his feet, as if he didn’t know what to say in response.

Parker sighed, and tossed the cigar into the trash can.

 “I’ve got a meeting to attend. I’ll be taking my leave.”

He stood up, and walked off without another word. Me and Fayes watched him off as he walked towards the end of the hall.

Reality. The greatest fear of the underground.

“Well… Nice meeting you Fayes.”

“Wait,” Fayes called, before I turned around.

He batted his eyebrows. “How many times have you been above?”

 “...Twice now.”

“Are you ever planning to go again?” he asked, stroking his chin.

I shifted my feet. “Maybe tomorrow.” Did…

“If possible… Could… I come with you?”

Why? Why would he…

“My trips aren’t that interesting.”

“It’s alright. Don’t worry about that.”

What am I supposed to say? No?

Our eyes locked.

Would it hurt to bring him along?

There was a desperation in his eyes, maybe a plea.

“I… suppose it’s fine. Meet me at the gate tomorrow at 3:00PM.”

The corners of Fayes mouth twitched upwards. He nodded. “ I’ll be sure to arrive on time.”

He walked past me.

“Later. Luke.”

The sound of footsteps got quieter and quieter.

I turned around. Fayes had left.

Why would he…

It wouldn’t hurt, I suppose.

- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - 

I took the last bite of the sandwich I made.

Lunch. 

Above. Above. Above.

I flipped on my IDS.

[Screen]
January 5th, 2051,  1:44PM
Welcome back, Luke. 

Swipe up to unlock.
[Screen]

An hour or so till…

I closed my IDS. In my view, were the flipped down photo frames. Lying across on the shelf, collecting dust.

Something left to save

I exited the room. 

The same marble floors and walls stretched ahead of me. They didn’t look the same. The white with black specks now looked like a simple sheet of gray.

People learn fast, when exposed to a new color set.

Above.

When I approached Parker’s desk, he was there talking to a person. They wore a dark blue cap and a black sleeve.

“There you are!”

I turned around.

Fayes walked up to me, his hair swaying as he took his steps. 

“Are you ready?” Fayes asked. He walked past me and pushed open the gates.

In front of us, was the same stairway. For the first time, I noticed a small sign printed on the wall. ‘Stairway to heaven’. Shaking it off my mind, I turned back to Fayes. 

I took my steps up. Fayes followed behind me.

“These stairs, they go much higher than the one below…” Fayes gripped the railing as he staggered.

A stairway to heaven was going be a long climb

After climbing the stairs and the bathroom, we entered the park.

The wind blew against my face. The sun shone upon us. Two things that would never be found below.

“Green… Blue… I haven’t seen these colors in forever.” Fayes muttered.

When I turned towards Fayes, he was staring at the horizon. His eyes were lost in thought.

I stepped forward. Fayes followed me.

“Yellow. Red. Pink. So many different T-shirt colors,” Fayes said, scratching the back of his head.

My fingers gripped the edge of my shirt. “A lot more things exist here.”

People hustled around. Crowds of people moved from one place to the other. People scooted from the bridges above us, from one building to another, a direct link.

“Ibis City, where one finds freedom,” I repeated.

Fayes blinked. “That… was the city slogan, wasn’t it?”

I nodded.

“I wonder…” Fayes looked away. His eyes locked to the ground. “What made you decide to return up here?” he asked, chewing his lips.

I stared at the sky. 

Fayes and I… weren’t different at all.

The underground place. Having lost everything, we had no choice but to come down to “live”, in a belief that it was different than dying.

The clouds inched across the sky. They never stop, no matter what, do they?

Amira’s face popped into my mind. 

Something left to save

That voice…

Princess. Ken. Tam. Them. We. Us.

What made me return?

I slid my hands into my pocket. “Maybe… Hope.”

“Hope for?”

“A hope that life will save itself.”

A moment of silence etched between us as Fayes digested what I said.

“A hope that life will save itself,” he repeated, kicking a rock. “Isn’t that just all of us down there?”

“Probably so.”

We walked in silence. On our walk, billboards flashed as they changed from ad to ad. News of the REVERSIBLE couldn’t be seen anywhere.

Fayes turned to me. “Luke, have you been out of the city?” he asked.

“Maybe once.”

When I looked up to face him, I noticed the place we were in.

My blood ran cold, and my eyes widened.

This place…

A sickening whisper started in my head.

Many skyscrapers stretched above us. But one in particular, stood out. The yellow star on top.

The sounds of sirens blared. Several gunshots echoed the scene.

A sickening feel erupted in my stomach, as if I was shot. I leaned forward, clutching it.

This place. Where… Where… 

You. Attempted to. Leave. She.

The whispers got louder, echoing in my head. A sharp pain started in the back of my skull.

Shot. Dead.

I clutched my head. The world spun around me. Voices around me muffled, as if I was underwater.

You should’ve been too.

Someone shook my shoulders.

“Luke, are you alright?”

I blinked a few times. When my eyes focused, I saw Fayes. He gripped my shoulders, staring at me. 

“Are you alright?”

The feeling in my stomach softened. I pushed myself out of his hands, before blinking a few more times. The environment hadn’t changed, those sounds were only in my head.

“Y-yeah.”

Fayes opened his mouth, but no words formed. 

I kept my eyes away from the building. “F-Fayes, let’s stay away from this route?”

Fayes glanced at the building, then back at me. He nodded.

We turned around. After a few minutes of walking, Fayes broke the silence.

“About that…” he asked. “What was that?”

“I almost never walk that way. Some… memory shards are left there.”

Fayes fixed his eyes on the ground. 

“Shards,” he repeated. “Memory shards.”

As silence stretched between us, the unsettling feeling stirred in my stomach.

I stopped. “W-well, I think… I’ll be heading back to the underground.”

Fayes glanced at me. “I guess I’ll go as well.”

We walked back to the park. The sun’s glare felt as if it was melting my skin. 

From zero exposure to high exposure.

We approached the bathroom.

“Back to black,” Fayes muttered. He stared at the ground.

After we climbed down the stairs, the empty, gray walls lined the room. Parker wasn’t at the desk. Several hoodie-covered heads, to which most keep down, lifted to see us return. 

“This is it, Fayes,” I said, pushing past the gates.

“Yeah…”

“See you. Fayes.”

I headed off without another word.

…

Fayes Drake. Something about him felt vaguely familiar. As if he reminded me of someone I once knew.
