\section{January 1st, 2051}
From the moment I woke up, there wasn't a reason to stay awake. 

“Open up! You have 11 months of rent due!”

There was pounding on the door.

“It’s a kid living in that room.” A different voice from outside said. “A 15 year old kid. No need to barge in.”

“We’ve already let him off the hook for 11 months. He should have plenty of money.”

“You don’t know that.”

“Hmph.” There was a shuffling of feet. “What do you want to do then?”

“Let’s ask the boss. He’ll know what to do.”

“...” In the moment, there was silence, silence of them leaving again.

I huddled beneath the warmth of my blankets. 

The footsteps were at the door again.

“Hey kid,” A voice called from the door. It was rougher, lower pitched than the previous two before. “Look, if you’re struggling in there, you still have to pay rent. 12 months kid, that’s the max left. Also, how are you getting your food?”

Silence.

“You know, this month and last month, I wonder if there even is someone in the room. It’s like a ghost room.” It was a voice from before. “Not even a sound. No one has come out, no one has come in for the past months.”

“Whatever it is, in a week, we’ll unlock your door and you’ll have to come out. You have \$3K due, but even if you don’t have enough money, at least inform us this isn’t a ghost room. We’ll make arrangements from there.”

There was a moment of silence.

“Come on guys, we’ll check back in a week.”

Footsteps. They had left.

I tossed and turned, trying to sleep again. Instead, my stomach protested with a growl.

I groaned, pushing myself up and turning on the lamp. The light illuminated the room, the cheap, white walls. Across, there was a shelf with several photo frames pushed down. I looked away and pushed the thought of them out.

My stomach growled again.

Empty bags of food scattered across the nightstand. I opened the shelf, finding nothing but a bag of bread with a single slice in it. 

The food I bought last year were all gone.

I put the remaining bread slice in my mouth. It was hard and stale like cardboard, like bread that was shelved for several months. Which it was.

A sharp kitchen knife layed next to the microwave. That dream last night.

Accept it and move on.

The words stabbed into me. I snatched my can of karocel, a drug. Empty. The pills I bought last year were all used.

I stared at the knife, a long, sharp blade of steel. A substitute for the pills. Escaping and destroying what was left.

I thrusted the idea out of my head, ignoring the pain in my stomach.

As I stepped out of bed, my legs stuttered and I stumbled. Taking a breath, I wobbled my way to the nightstand, grabbing my card. My legs shook as I headed to the door. 

When I opened the door, light flooded in from the hallway, blinding me. 

When my eyes adjusted to the light, the marble hallway with its concrete walls painted white stretched out in front of me.

Tired, I rubbed my eyes and leaned on the wall.

A boy wearing a black plaid T-shirt walked past me.

“U-um,” I tried to say. Instead, it came out as a raspy, dry sound.

He turned around, gazing at me with his gray eyes. “Do you need something?” he asked, wrinkling his eyebrows in confusion. 

“D-” I coughed, and cleared my throat. It felt dry and itchy, sore from months of collecting dust. “Do you know where the rent booth is?” I asked. 

“The booth?” He scratched his head and pointed to the right. “It’s that way. Go right, then up the stairs, and you should be at the booth.”

I gave him thanks and headed off. “One foot after another,” I thought as I staggered through the hallway, holding onto the wall for support.

The marble walls were cracked and old, symbolizing the place I was in. Underneath the city, people established an underground “mini-society” that was based on illicit drugs. 

I limped to the end of the hall, passing many doors, many people just like me. People that came down here.

Having lost everything, they had no choice but to come down to live on illusions, in a belief that it was different than dying.

I climbed up a stairway, arriving at a large circular platform. I panted, trying to catch my breath. My legs felt like giving in, soreness lingering in the back of my feet. I flopped down on the floor to catch my breath.

Vending stores lined up along the edges. People walked around. Some had a cigarette, smoking in spite of the risk to their lungs. Some were talking to another. Some were sitting in the corners with their heads down, as if trying to digest what once happened. All shared the dark, black shirts that symbolized the hopelessness of this underground place.

 It hasn't really changed since last time I was here.

My breathing slowed down, into its normal rhythm. I pushed myself up and continued down the path.

I met the end of the circle containing another stairway that went up. 

A stairway that led to reality. Above. Back to where I-.

I shut down the thought and took a deep breath, calming down.

I turned to my right and saw a rectangle table with a middle aged guy typing on what looked like a holographic monitor. He looked like was around his 30s. His dark gray T-shirt had a fine, red print, saying “Heaven is above, not below.” What an absurd thing to say. 

The signs around the table labeled that it was the rent center.

I walked over, coughing to make sure my vocal cords work.

“Hey,” I said, taking my IDS out.

Now that I had a closer look, he looked like he was in his 40s, his skin wrinkled. A mustache sprung from his nose. His name tag said, “LEADER, Parker”.

“Oh?” he asked, minimizing the hologram. “And who might you be?”

“Is this place for rent submission?”

“Yup, you got that right, if you haven’t already gotten it from the sign,” he said, pointing to the sign below the desk.

“Where do I insert payment?”

“Right over there,” he said, pointing to a slot.

I pushed the slider on my ID stick that slid open a mini card. I popped it into the slot. As it was processing, my eyes wandered to a mirror lying on his desk.

My dark, shaggy and torn up blue T-shirt hung off me, looking like two sizes larger than what I would normally wear. My shorts were filled with holes. My hair was a long, cluttered mess that reached my nape, looking like it hadn’t been groomed in years. 

There was a beep of the scanner.

“Oh? You’re Luke?” Parker asked. He turned to me and observed my figure, before furrowing his eyebrows. “Have you been eating at all? How much do you weigh?”

“I haven’t checked,” I replied, tapping my fingers.

“You’re the one who’s been in room 15 for a year?”

“Yeah.”

“You spent last year entirely in that room. Any plans for this new year?”

“...”

There was a moment of silence while Parker was typing my order.

“Alright kid,” he said, tapping the enter key. “Your rent payment is completed. Is there anything else I can help you with?”

“I would like to pay upfront for 12 more months. Also, I would like to buy a few more cans of karocel.”

“12?” Parker blinked, then glimpsed at my body. “Your body is not going to handle that again.”

“It’s alright, I’ve got the money.”

“And a few more cans of karocel you say?”

“Yeah.”

Parker let out a sigh. “Hey kid, can I ask you something?” He turned his chair and faced me.

“What?”

“What is it that you want?”

“I want housing and karocel.”

“Why?”

“... It doesn’t matter, please just let me buy them.”

Parker stared at me. His mouth opened, but nothing came out.

At that moment, a voice from behind me called in my ear.

”What a strange place to find you, Luke. I would’ve never expected you to come here.”

I turned around, but there wasn’t anyone. Not a single person was walking around. Only vending machines, beeping and buzzing to attract customers.

“Am-. She wouldn’t have ever wanted this, you know.”

“Who are you?” I called. My vision blurred. The objects in front of me faded into a fog.

“Luke. You’re not doing anything for her by living like this. This was never her wish.”

The line triggered a sharp memory somewhere in me. My stomach ached for relief.

“She’s… dead.” I reached for the counter, but there was no pill of karocel. 

“You’re going to dismiss her simply as dead?”

I cupped my ears and kneeled down. My heart pounded in my chest.

The voice continued.

“When you die living like this, and meet her, what would you say to her? ‘You loved her so much you couldn’t live without her?’ That’s a sweet, cheesy line, but she wouldn’t have appreciated it.“

“Please… stop.”

The voice was silent for a moment.

“Luke. There are things you still have left to save. There is something left to save.”

The presence faded. The blurry images sharpened, and I could focus again.

“... Luke?” Parker asked. “Are you alright?”

I slowly got up, my head throbbing. There was a sharp pain in my heart.

“Luke, I’m going to do a blood test for karocel.”

I shook my head to clear my thoughts. “What?” I asked.

“It seems you’ve been taking too much karocel in the past year. Hallucinations, etc. I can’t legally prescribe without a blood test.”

“Have we done ‘legally’ here?”

“It's for safety reasons. Not the law.”

I chewed my lips.

“There’s no punishment. It’s a mere test that won’t harm you,” Parker clarified.

I gave in and nodded. He took my IDS stick out and walked us to behind the office into a room.

There was a table in front of me, with a metal sensor arm.

“So…” Parker was looking at his [“Phone”]. “Alright, sit here.” He pointed to a chair and a table. The table had a blood drawing sensor arm. “It only needs to touch your skin.” Parker said, looking at the screen.

I sat down and put the machine arm against my arm.

“230!?” Parker pressed his hand against his forehead. “That’s a high reading…”

“It was the only way to relieve. Revive”

“Revive that she you were talking about?”

“...”

“Look, there’s no way I can give you more. The safety line is 100. Your lifespan will be shortened by at least 15 years by having that concentration for a few months.”

“I don’t care about that lifespan.”

He stayed silent. “Well, I still can’t give you the karocel.”

“Can’t or won’t?”

“Both. Legally obligated not to, and morally wrong.”

“That’s fine, I guess.” I moved the arm, standing up to leave.

Parker didn’t seem to mind, instead, just laid back in his chair.

“Man, you came here 2 years ago. You were 13 years old at that time.”

I stopped. “Is there something you want to say?”

He took a cigarette and lit it. “No, not really. I just remember the look on your face when you came down here. You still had fat on you at the time. Your clothes were still clean, and you didn’t have hair that was so long.”

“That’s all water underneath the bridge now.”

He laughed, putting the cigarette into his mouth, and blew out some fumes. 

“I don’t suppose you have the strength to continue your old job? With a body mass like that, it’s easy to tell you haven’t been moving much or eating enough.”

“... You want me to continue my old job?”

“No, that’s not it.” He paused, as if a thought suddenly occurred to him. “When you came here, you’ve never told me, where’s your parents?”

His question triggered a distant, faded memory.

“They’re… gone.” I turned away. “There’s nothing above for me to return to.”

“Your parents died?”

“Something like that.”

With that, I headed towards the door.

“... Fine. Take these.”

I turned around to see Parker holding out a can of karocel.

“There’s 5 in here. I won’t give you any more.” He tossed me the can. Inside the orange cylinder were 5 of the familiar white, oval pills.

“Take care of yourself, kid.” Parker threw his cigar into the trash can, turning around. “I’ve got to go back to my job. Make sure you eat well.” He stood up and walked past me.

I watched him off, before slipping the can into my pocket. I left and approached the same stairs that led above.

Try something new. Something left to save.

Her voice and that voice kept echoing in my head.

“Why?” I asked. “Why did any of that have to happen?”

I stared at the stairs.

A world above. One that takes. One of no recovery. One of misery. Yet something about it intrigued me.

I lightly pushed the gates. They swung open with ease, as expected.

…

The moment I stepped up, my legs were greeted with a sharp pain. I pulled back my foot and stared upwards into the seemingless endless spiral stairs.

New light. That place above.

I shook my head and walked away from it. Maybe tomorrow.

I headed towards the markets, looking at the menus. My stomach growled.

I stopped by a counter, one that looked like it was selling produce. A digital screen displayed what was on sale.

(Screen) \\
Food list \\ 
(Screen)

I tapped on a few buttons to order some bread, ham, tomatoes, water, and milk jugs.

An arm moved inside the vendor machine.

“Total: \$19.99 + 0.60 (3\% Tax), \$20.60”, the screen displayed with a beep.

I plugged my IDS card in.

“Thanks sir, you’re good to go,” it read. The packaged food slid into the pickup basket. I wrapped it all in a bag, leaving a slice of bread out.

I limped towards my room with my groceries.

Everything I needed was with me. Food, water, some karocel… The things I needed to stay in for another 5 days.  But the idea felt hollow. As if I wanted something else. Something else, something contrary to the old schedule.

I pushed open the door and entered back into my room. The same, dim-lighted gray walled room. I put my groceries into the mini-fridge, and laid on my bed.

Their voices stayed in my head. Amira told me to find something else. Move on. But how could I do that? I wanted everything back. Everything that was taken that day.

Was there anything for me left to find? There was nothing left.

Something left to save.

I took out the can of karocel from my pocket.

She probably didn’t want me to be engulfed in this life forever. But who was that voice earlier? How did it know my sister? How did it know who I was? Maybe it was a hallucination. I rubbed my forehead. 

Something left to save. 

What in the world was that voice talking about?

The guy at the counter, Parker, told me I would probably be dead soon if I kept using these.

But why did it matter? There was nothing to care about if I died.

I popped the pill into my mouth. Instantly, a feeling of warmth and relaxation came into me. But something was different. She didn’t appear in my mind. 

The warmth was just like the old pills. But it was weak. 

I turned over and slid open the cabinet. No pills were left, nothing to compare to.

It couldn’t be possible that I used too much for it to be effective anymore?

Maybe Parker would know what was happening. As I rolled back, a sharp pain spawned in my legs. “Oww…” I murmured. I stared at the ceiling. 

Probably should rest up. I closed my eyes and my mind drifted off.

