\section{Fresh Starts Don’t Exist}
I held on to the door stall of a bathroom, trying not to fall over. My stomach felt like giving in. 

She…

Resisting the urge to throw up, I took a deep breath.

In. Out. In. Out.

I flopped down on the floor. As I sat there, panting to catch my breath, my mind raced.

Why was she there? Did she remember me? Even if she did, there is no way she should be able to recognize me. After all, my physical appearance completely changed.

I stared at myself. My skin was at least several shades paler, my arms looked like one half of the width they used to be. I grabbed a strand of my hair by my neck. My hair was long to the back of my nape. I was wearing a hood too. There shouldn’t be any way for her to remember.

She couldn’t have known I was there.

My breathing slowed down, the nausea settled down. My mind still spun, but I felt a lot better. Not enough…

“There’s no way I’m able to walk back…” I took off my hood, staring at the ceiling of the bathroom. “Something left to save, huh?”

I closed my eyes. 

How was I going to return?

A few more minutes, I thought. Maybe I’ll be able to walk.

…

She still wore that light purple ribbon. It looked torn up and old. It still had that grape juice stain from years ago.

She was definitely Princess. She was alive, at the mere least. I wonder about her brother…

Something left to save. Something isn’t a person. Something is a concept. A memory. A way for the past to move into the future.

I opened my eyes and took out my can of karocel.

It didn’t have much effect on me, except as a calming substance. 

I had no drug stronger than karocel. If I lived underground, I wouldn’t be able to get anything.

But… I could try to save the present. Amira was gone. Mom was gone. But Princess, Ken, Tam, dad… was not. Maybe… I could somehow make things like the past again?

I laughed inwardly at the thought.

The odds of the second one were extremely low. People move on. They forget. They may have found a new “happiness”. To show up in their lives again, after being the reason their old happiness was lost; the idea made me laugh.

I pushed myself against the wall. My legs shook as I stood up.

There was nothing for me to do right now. Nothing left but me to return to the so called hell.

I wobbled my way out around the building I had run into.

The crowd from before were cleared. The stage was empty; the speakerman left with his equipment. Princess was nowhere in sight. The only thing left was the idle sound of people moving and the wind blowing. 

I turned around, walking towards the park. 

When I returned to the park, it was dimly lit, with nothing but the street lamps that were there. They were spaced a lot, so there were plenty of dark sections.

After the walk, I stopped in front of the bathroom. 

Back to the underground. Away from everything. A place to run away, away from… reality. 

I turned around and looked at the dark, night sky behind me.

The city lights shone brightly. Despite being in the park, I could see the colorful signs and billboards from the city. 

The city was reality. Colorful, filled with positive colors. But also filled with negative colors. Underground, lack of color. Little negative colors, but little positive colors either.

I closed my eyes and held the knob. 

…

Up. Above. Heaven is above, not below.

That quote… I couldn’t help but laugh. If heaven existed, it isn’t above. Space is above. Not heaven. Wherever heaven is, I have no idea.

Before I turned the knob, a voice came from behind me.

“Well, well, well, look who it is.”

I blinked, my hands letting go of the knob as I turned around.

Two people wearing shaggy black T-shirts were looking at me. They carried bats, and wore sunglasses. One of them took off his sunglasses.

“Luke, wasn’t it?” he asked. “Remember me?”

“Who are you?”

“You don’t remember us…” he shook his head, then laughed. “Of course you wouldn’t. Maybe you will, after I serve you revenge.” He lifted the bat off from his shoulder.

I scooted back and braced for the impact, but the guy in the middle extended his hand in front of him. “Stop,” he said.

“You don’t remember your victims at all…” the guy muttered, lowering his bat.

Who were these people? They acted as if I should remember them.

“Enough, Jack,” the guy said. He turned to me. “We’re here to collect revenge funds. Protest and you’ll get the bat.”

“Revenge funds? For what?”

“...Of course you wouldn’t remember,” he mumbled, scratching his chin. He looked back at me. “Well to you, then we would just be robbers. Empty your pockets,” he demanded, pointing his bat at me.

“What do you want from me?”

“Empty your pockets. Now.”

I slowly reached into my pockets, pulling the insides of them out. Nothing but my IDS.

“Cabe, that thing holds ten dollars at most,” the one named Jack muttered, tightening his grip around the bat.  “I’d rather just beat him up.” 

Cabe didn’t flinch. “Hand it over kid. Your IDS.”

\$21K actually, was in the IDS. 

I hesitated. It was the money my dad left me. Also… There’s things on this IDS that couldn’t be replaced. Like… certain pictures.

I pressed my back against the door. 

Cabe snapped his fingers. “Look kid, hand it over. I’m not playing with you,” he said, tapping the bat on the floor. “It’s to pay back revenge for crapping us. My fellow Jack here wanted to floor you for it.”

“My job…?” I asked. My heart pounded in my chest as I tried to recall memories. 

Were they one of…

“Hand it over!” Cabe snapped. “I’ll give you 2 seconds.” He lifted the bat. Jack eagerly followed him.  

Instead of handing my IDS over, I closed my eyes.

“One.”

The wind blew, a refreshing, cooling, air breezing against my face. 

The thought of dying the next second. A bat swing can’t be enough to kill, but my mind wandered to the thought anyway.

As I stood there, the second felt longer than a second. As if time stopped. The bat never came. 

I slowly opened my eyes.

A figure was standing in front of me. Jack and Cabe were knocked down on the ground in front of me.

“Who the heck are you?” Jack asked, scrambling for his bat.

The figure extended something out of their sleeve. It was a sharp weapon. The sight of it sent chills through my veins. I knew what it was, something that I wished I didn’t.

Jack and Cabe stared cross-eyed at the blade, their faces in horror.

“Get out of here. Or else your lives might not be intact.” The figure flashed the blade at them.

Jack and Cabe nodded, turning around and fleeing. As they ran off, a symbol on the sleeves of their shirt, an ibis bird with the number II scribbled on it.

That symbol. WINGS II.

The figure standing in front of me took off their hood. Without it, I could see clearly, it was a woman. She looked like she was in her mid 20s. Her black, smooth hair fell to her shoulders as she turned to me.

“Are you alright?” she asked, sheathing the weapon back into her sleeve.

“...Who are you?”

“Harmony Summer. Or just Summer,” she suggested, brushing some dust off her clothes.

“W-why…” I stammered, struggling to get the words out. 

Why did this person have one of those?

I took a deep breath, staring at the ground.

“Why do you have one of those? Those K wea-”

The word stuck in my throat. It felt wrong in my throat. I swallowed the remainder of the sentence.

“One of these?” Summer asked, sliding the sleeve. The sharp, silver blade revealed underneath. She peered at me. “Why would you know what this is?” she asked, her tone sharpening as she narrowed her eyes.

Something about her voice made me feel like she would kill me if I didn’t explain.

“Because I’ve…” My voice faltered. “Experienced them before.” As a memory flashed in my mind, my hand drifted to my shoulder.

Summer stared at where my hand was. Her expression softened as she sheathed the weapon. “Never mind then,” she replied. Turning around, she scratched her chin. “I wonder why they would go after you. It’s not like you were particularly special to them. Did you know who they were?”

I took another deep breath, settling myself. 

“Y-yeah. They might have been some people that I…”

It was last year, one of the tasks for my job. The last one. They still remember what I wore and did. 12 months ago, and they’ve never seen me since. Despite that, they still had such vivid memories.

“I… I had to go through to do something.”

Summer nodded. She must’ve noted my unease, because she stopped pressing. “What’s your name?” she asked, changing the topic.

“Lu-” I hesitated. 

The news reports were probably gone now. Besides, many people probably share the same first name.

“Luke.”

“Luke,” she repeated. “Nice to meet you, Luke.”

Our eyes locked. Her green eyes gazed into me, as if trying to see into me. 

Summer closed her eyes and looked away.

“There’s some matters I have to go to now,” she said as she turned around. She gave me a wave. “See you around. Luke.”

“See you…”

Summer walked off towards the city, sliding her hood on.

I turned around and opened the bathroom door. Finding my way down, I stepped down the stairs.

Much like everything, down was easier than up. The thought gave me an urge to laugh. 

As I approached the bottom, the gates stood in front of the same, familiar, underground place.

Contrasting the colorful above, the place looked like a monotonous sheet of black and white. Parker was still absent from the desk.

“Heaven is above, not below,” I repeated.

Above, not below. Above, not below. Above, not below.

I pushed open the gates. Cabe… Jack…

Something so small, but they remembered the details of that interaction.

If that was true, then maybe it was possible.

That they would remember. Remember it all.
That there was a chance after all. A chance for return.
That there is something to save. A time to save.

That there is hope, that we can be together again.