\section{A Different Warmth}
I opened my eyes. The room I was in was still lit. 

I sat up on my bed. That karocel gave me no dreams, no illusions. I rubbed my eyes. My legs had a slight sore in them. They haven’t recovered, I suppose.

My stomach had an ache in it, a burning feeling. Ah, I was starving.

I pushed myself up and ate a slice of ham.

The taste of the smoked ham reminded me of the last time I ate meat. Instantly, my stomach felt significantly better.

I wiped my mouth, opening the holographic phone-like screen from my IDS. It stuttered and flickered at first from not being used in months.

[Screen]
January 2nd, 2051, 6:21 PM
Welcome back, Luke. 

Swipe up to unlock.
[Screen]

I swiped the hologram. A lock button showed up, requesting for a password. Having forgotten the password, I opened up the security hint.

“What was the name of your sister’s best friend? Age?”

My sister’s best friend. The voice’s line echoed in my head. Something left to save.

I entered in the passcode of “PRINCESS.14”

The lock screen faded and replaced itself with a photo of my sister and I taking a picture at a park with 3 others.

A feeling of emptiness and pain filled my heart. Impulsively, I dropped the IDS stick, the hologram flickering out as it hit the floor.

What was that feeling just now? I shivered, shaking my head. It wasn’t a good idea to use the device. I picked it up and put it in my pocket. 

Something left to save.

The idea of going above popped into my head. But I could only laugh and ridicule the idea. What was up there, after all?

But I found myself sliding open the second shelf of my nightstand. There was a sweatshirt and a T-shirt. Torn, but acceptable.

After taking a shower and changing into the clothes, I slid the can of the pills from yesterday into my pocket and entered the hall. There was no one today, the hall was bare. 

As I walked by, I observed some paintings on the wall. One depicted a hell being below, as going towards the core of the Earth makes temperatures hot. Like the temperature of Hell. Painted by Parker Shawn. Of course it was the same guy wearing that T-Shirt. Many must’ve liked it, because it had a good amount of coins in the donation box below.

I approached the gates on the upper floor.

Something left to save.

I grabbed the gate, but my arms shook violently, refusing to push them.

A whisper started in the back of my mind, warning me against going up.

I looked around the hall, but no one was here. My eyes wandered to Parker's desk. The desk had no one. On a label at the top, it said “CLOSED”.

No one was here.

I turned back to the gate. My head felt strange. A part of it desired to see what was going on above, yet the other wished for a flight back to my room.

I put my hands on the gate. It felt fragile, like a simple push would break it off the hinge.

Was I going to do it? Did my legs feel alright?

Maybe. Just once. I thought. 

I pushed open the gate, the gates flew and hit the wall. Past the gates, the stairs stretched to what seemed to be infinitely upwards.

“... Something left to save?” 

Was there?

Tam… Princess… Her brother…

I hadn’t ever checked what happened to them since then. They’ve probably forgotten me. It’s been 2 years, after all. Was it something left to save? 

I wonder if my dad was still alive. After mom…

I took the first step. My body shivered, as if it was against everything that I was doing. Some part of me wanted to flee down the stairs and run back under my blankets. But yet, their voices rung in my head.

Something left to save. Moving on.

I took another step. Then another. Then another. Each step felt different. With every step, my nauseous feeling grew stronger. Yet, their faces appeared more clearly in my mind.

“...”

Amira. Mom.

My legs started to get weary. The nauseous feeling was getting worse. I stopped and leaned on the wall. My breathing was heavy. Panting, I turned around.

The gate that I had climbed below was gone. Infinitely below. 

I took another step, looking forward. It didn’t change anything, the staircase stretched endlessly above. But I couldn’t go back. 

I continued my way up the stairs.

The excruciating pain in the back of my leg. The whispers in the back of my head, warning me to return back underground. I ignored them all.

I wanted to run underground, hide from everything, but I also… wanted to see the world again. I had to see the surface again

At last, I reached the top of the stairway. In front of me was a simple door. 

That was it. The final obstacle.

I sat down on the floor, trying to catch my breath.

“It’s been 2 years, hasn’t it?” I asked. 

No one but the echo of the hall responded.

I pushed myself back up and gripped the door knob.

Try something new. Something to save.

I pulled open the door. 

The rusty smell of metal filled the air as I climbed into the bathroom. The white, shiny granite floor was clean, along with the sink and toilet. The hatch closed behind me. I walked towards the door of the bathroom and opened it.

Warm, orange sunlight shines into my face. The blue, cloudy sky stretched on forever above me. In contrast, the green grass and trees stretched around the park. There was a group of children, playing in the empty field. They ran around, tagging each other. They would laugh, smile, and go back to running after being tagged. Their parents would smile and take pictures of them.

At the end of the lawn, the skyscrapers stretched outwards to me. 

Ibis City.

…

I slid on my hood and took the path for the city.

2 years…

Many things have changed. The small trees in the park years ago had grown into fine, tall trees. Banners lined on certain paths, informing walkers of construction.

I stopped. The picnic table in front of me felt familiar. I brushed the brown, wooden surface of the table.

A drawing, yet faded, was still on the table. A drawing of a boy playing with his toy car.

A memory clicked in my head.

“Thankfully, you didn’t get in trouble.” A boy talked to his younger sister.

“I know, I’m sorry… ”

“It’s alright, Princess,” A different girl said. She brushed Princess’s hair, giving her a soothing smile. “I’m sure they understood.” 

“... I’m really sorry.”

“No need!” She laughed and patted Princess’s back. “Just ask before you do.”

The boy let out a small smile. “It’s alright, no one got in trouble. Just be mindful when doing things on other people’s things.”

Princess gave him a weak nod, before turning to a different, smaller boy, who was playing with his toy cars. She watched him play with the cars whilst the others were talking about a different boy that didn’t show up, one who had to complete some homework.

I looked at the drawing again. It was still there. A drawing of a boy playing with a car. 

That was the past.

I stepped away from the table, and continued back towards the city.

The fresh, cold air of January blew against my face. The busy, noisy city sounds of people hustling. The sound of the car engines as they drove. I approached the end of the park. In front of me was the city.

The white, silver, light blue skyscrapers stretched beyond me, into the sky. The streets and the sky bridges connecting buildings were filled with people. Some rushed; they were late for something. Some cheerfully talked to their friends. Colorful ads on billboards constantly changed, along with the atmosphere of the city.

It’s been a while since I was here.

I walked along the streets.

Princess, Ken, Tam, Dad. Was there anything left?

I wondered if there was any way to check.

On a billboard above, was a TV. It was a news report about-.

I stopped.

“Yesterday at 11:49 PM, there was an assassination in (Building). 4 armed men with K-series weapons broke into the building, and killed Prime Minister Gale along with his 2 bodyguards and severely injured one civilian. Current police investigations are suggesting it was done by the terrorist group REVERSIBLE.”

I closed my eyes and walked away from the board. 

Again. It happened again. Things haven’t changed one bit.

I met a clear, transparent door to my left. The entrance to an apartment. My old apartment complex. I lived here. Before…

I pushed open the door.

The shiny, white floor. The white walls. The golden chandeliers. The glass railings of the above floors. It was the same place as always.

I wonder if dad…

I walked towards the elevator, passing through many people on my walk. They contrasted vastly to the underground place. 

Some were younger children, talking and laughing on their way out. Some were older, returning home from work. Some wore white shirts, some wore red shirts. Some wore blue. There were countless colors. Some wore ‘our’ black shirts too.

Heaven is above, not below

I paused at the elevator. It had the number 7 etched in gold above.

I hit the button.

The elevator doors opened, revealing the white box with golden handles.

I stepped in, tapping the 3rd floor. The elevator started to go up.

I brushed some dust on the handles. A memory of me riding this elevator down flashed in my mind. My last ride.

The door opened. I stepped out.

After a brief walk around, I stopped by a blue stained glass door. Behind was a silvery white metal second door.

Room 102. I haven’t forgotten that number. I took out my IDS. 

Would this still work? Why would dad keep my IDS still in the system? Was this even his room anymore?

I tried the IDS. The door beeped green, signifying it was unlocked.

Did dad still own this place? Why would he keep my IDS in the system? Would he not be afraid if someone got my IDS and got in?

…Then again, I guess he wouldn’t.

I slid open the door and walked in.

The dark, brown wooden floors were stained light yellow. Empty bottles of wine, beer lay around the room. On the counter was a box of beer cans. 

He was alive, but… nothing changed.

I kneeled down, picking up one of the empty bottles. It reeked of wine.

Did I want to leave him like this?

I walked to a table. There was a soggy, old, ripped piece of paper. Strangely, it had writing on it. I looked at it closer.

[Letter] \\
A letter I wrote to clear my mind.

Dear son. \\
\indent This note will probably never reach you. Whenever you’re dead, alive. It's unlikely you’re ever going to come back to this place. Leaving the door open to your IDS, it's a belief that you’ll ever come back. There’s nothing to lose, I’m already nothing. Despite everything, I wish… that if you’re alive, you’ll live someday to recover. If you die, I wish you died without guilt. 
					
\begin{flushright}
    Regards, Yarold \\
    October 11th, 2049
\end{flushright}


I stared at the letter. It was written almost 2 years ago. Months after…

…

I took a black marker on the table.

\textit{I’ll try. L.E}

Setting down the marker, I walked into her room. 

The moment I entered, I shivered. Even though the temperature did not change, the air felt colder.

Her desks were covered in dust. On her desk were her notes and an open textbook, her notes scattered across it. 

A test she never took.

I closed my eyes and took a deep breath.

…

I opened my eyes. A purple hairpin lied on the textbook. I walked over, and picked it up. Her hairpin. I brushed the dust off it. There was a snowflake pattern. She liked snowflakes ever since I could remember. 

I slid the purple hairpin into my hair. 

It was time to go. After locking the door and navigating out, I took a deep breath as I exited the apartment complex.

The sun had set, the lights of buildings turning on. Green, red, blue, lights illuminated the city. Night did not stop people, as they crowded streets, taking pictures, laughing with each other.

I walked towards the park.

Was there something left to save? My dad was alive, but in the end, I was just a spectator, who lost everything, pretty much even his own life. 

“To our dear Minister…” a microphone announced in front of me.

I turned to the direction of the sound.

There was a gathering. People crowded before a stage. Their heads were down, as if they were praying at a church. 

I stared across at the board. 

(Board) \\
To Minister Gale,

We are thankful for your service. You have undoubtedly done many great things that we’ll never be able to pay you back for. Unable to repay you, the least we can do is mourn and show our gratitude.

For the 5th tragedy that has happened at the hands of REVERSIBLE.\\
(Board)

A ceremony for that REVERSIBLE attack?

There was a nauseous feeling settling in my stomach. I stepped closer to get a better look. 

For the 5th tragedy that has happened at the hands of REVERSIBLE.

There have been 3 tragedies between that day and today…

No civilians were killed this time. Either that REVERSIBLE has improved at their ability to kill only who they focus on, or security was improved.

Still… 

If only it was like this that day. No civilians killed.

I pushed the thought out of my mind. 

Things that happened, happened. There isn’t an if. 

I observed the crowd, trying to clear my head. I’ve never been to one of these, despite being one of the victims.

As people passed by the crowd, they tried their best to remain silent. In the crowd themselves, people were quiet. Some were probably grieved, although some others were probably just trying to get through. 

As the speaker began the tribute, I closed my eyes. The world disappeared, the voices fading in the background.

The wind blew against my face, leaving a swish sound as it went by. Time seemed to pause. I felt my heart beating, pulse by pulse. Inhale, exhale. It felt peaceful, calm, as if I had nothing to worry about. 

Finding something new. Moving on. Her words haven’t left me. But…

No. I won’t. There’s something I still have to do before I leave.

I opened my eyes. A group of birds flew above us. My legs seemed to feel weaker.

“Thank you. Everyone.” The speaker wiped his eyes with a handkerchief. 

There was a bare mumbling as the group departed. Instead of leaving, I stayed where I stood. 

I couldn’t bring myself to move. I stared at the people departing. But there was something that caught my attention.

My eyes widened and my breathing stopped.

In the midsts, a familiar pair of amber eyes flicked past me. In her shoulder length, brown hair, now dyed with streaks blue, was the same light purple ribbon. Her light gray jacket fluttered as she walked.

She stopped walking, as if she noticed something particularly odd with her situation. When she turned her head to look around, our eyes met.

It was definitely her. The same glint in the eyes. The same fire. Even though it seemed put out. She gave a confused stare, as if she was wondering why I was staring at her. Yet also a spark of curiosity, as if her brain was trying to comprehend the sight of me.

Words popped in my head, almost like all my thoughts from the two years flooded my head.

There was a strong nauseous feeling, my head felt dizzy. My mind didn’t seem to like what was happening. I wasn’t ready. Not yet.

Instead of saying something, I turned around and bolted, doing my best to avoid running into people. 

It might’ve been my imagination, but I might’ve heard her calling “Wait!” behind me as I ran.

Not now… Not yet…
